Discrete Ordinates

### 2017-05-05 docprep/chapbib.tex
Added a new chapter - results.

This section is the literature review. I do these things.

\section{Introduction}
Many different things are required.

\section{CT Dose Estimation}
How is this done now?

@@

Two phantom datasets are used in this work.

\section{Discrete Ordinates}
Discrete ordinates are old. The book is \citet{ref:lewise}.

>>>>

This chapter summarizes the literature reviewed in preparation of this work. The literature review is split into multiple sections, each highlighting relevant works pertaining to a particular component or section of this work. The first sections cover introductory work and steps necessary for preprocessing data. Section~\ref{sec:discordlit} covers historical and recent work in discrete ordinate methodology, the methodology used by DOCTORS. The remaining sections cover GPU hardware and other implementation facets.

\section{CT Dose Estimation}
The dose a patient receives form both diagnostic CT procedures and radiation therapy is of great concern to the medical community [CITE].

Monte Carlo codes have been used in the past to compute flux-to-dose conversion factors for a reference person [CITE ICRP].

@@

Two phantom datasets are used in this work [CITE].

\section{Discrete Ordinates}\label{sec:discordlit}
Discrete ordinates are old. The book is \citet{ref:lewise}.

### 2017-05-05 docprep/chapconc.tex
Updated the thesis chapters and the beamshapes figures
Added a new chapter - results.

This appendix covers the math for Legendre polynomials and spherical harmonics

\section{Legendre Polynomials}

They exist.

\subsection{Spherical Harmonics}

They also exist.

The real harmonics. The even/odd harmonics.

The addition theorem.

>>>>

Conclusions.

\section{First conclusion}

I concluded many things.

\section{Future Work}

A number of simple modifications to DOCTORS could be made that would greatly increase the code's usability and robustness. One of these modifications, generation of more refined group structures, is not a change to DOCTORS \textit{per se} but rather a change in the input cross section data. The other changes are additions to DOCTORS that would add new capabilities to the software.

In addition to specific modifications, some additional, broader future goals can also be identified.

\subsection{Group Structure}

The cross section data currently used by DOCTORS are taken from SCALE6.2. While these cross sections have been found to be sufficient to produce flux distributions in medical CT imaging, a more refined group structure designed for medical applications would be worth investigation.

This work can be done using either NJOY [CITE] or the newly released AMPX [CITE] code. Either code has the capability to collapse an ENDF formatted data file into a group structure of the user's choosing in the format DOCTORS reads.

NJOY or AMPX.

\subsection{Temporal Extension}

Use 4D CT to do temporal stuff as well as spatial stuff.

\subsection{Multileaf Collimation}
Collimators!

### 2017-05-05 docprep/chapmeth.tex
Added a note about convergence and a figure for beam angles.
Added a new chapter - results.

@@

@@

>>>>

\subsection{Convergence Criteria}
The typical converence criteria used to determine whether or to terminate further iteration is the maximum relative error from the $i-1^{th}$ iteration to the $i^{th}$ iteration given in Eq.~\ref{eq:conv}. Once the relative error in the parameter of interest, $\phi$ is below some threshold, $\epsilon$, the iteration stops and the solution is considered converged.

\begin{equation}\label{eq:conv}
\frac{\phi_i - \phi_{i-1}}{\phi_i} < \epsilon
\end{equation}

In some problems, the convergence criteria given in Eq.~\ref{eq:conv} is not reached for many iterations. In these cases, terminating the solution early rather than waiting for full convergence is appropriate. This is enforced by a second criterial. Whenever the number of iterations, $i$, exceeds the total permissible number of iterations, $I$, the iteration is terminated.

\begin{equation}\label{eq:conv2}
i > I
\end{equation}

Under further investigation, the cause of the convergence failure that results in Eq.~\ref{eq:conv2} being exercised often stems from floating point error. The flux magnitude fluctuates wildly in regions of very flow flux, such as the gantry. In these regions, the relative uncertainty will remain much higher than in regions with smoother flux distributions. FIGURE XYZ SHOWS.

In order to measure the uncertainty due to floating-point error, another convergence criteria was added. Rather than looking at the relative change from iteration to iteration, the total absolute change is measured, computed by Eq.~\ref{eq:conv3}. The termination criteria is given by Eq.~\ref{eq:conv4}. Computation of a value for $\epsilon$ requires two previous iteration, thus this condition cannot be met until the third iteration and thereafter.

\begin{equation}\label{eq:conv3}
\epsilon = \sum_{\vec{r}} |\phi_i - \phi_{i-1}|
\end{equation}

\begin{equation}\label{eq:conv4}
\epsilon_i > \epsilon_{i-1}
\end{equation}

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/beamconexy}
        \caption{Cone xy}
        \label{fig:beamconexy}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/beamfanxy}
        \caption{Fan xy}
        \label{fig:beamfanxy}
    \end{subfigure}

    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/beamconeyz}
        \caption{Cone yz}
        \label{fig:subsweep_general3}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/beamfanyz}
        \caption{Fan yz}
        \label{fig:subsweep_general4}
    \end{subfigure}

    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/beamconexz}
        \caption{Cone xz}
        \label{fig:subsweep_general5}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/beamfanxz}
        \caption{Fan xz}
        \label{fig:subsweep_general6}
    \end{subfigure}
    \caption{The beam shapes.}\label{fig:beamfancone}
\end{figure}

@@

Talk about the MCNP generation in the comparison to results part.
